Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-08 paper/paper.Rmd
refine ' mlr3spatiotempcv within the mlr3 ecosystem' section' (#126)'

Within \pkg{mlr}, partitioning strategies are represented by resampling objects (correct?) of class xyz, which are generated within mlr3 itself (for regular random CV, correct??) or within specialized extensions such as mlr3spatiotempcv.
In the ML pipeline, these objects are used for model assessment by ... objects/tasks/whatever and for model selection by ... objects/tasks/..., providing a consistent framework for both tasks that is necessary to optimize learners for a given prediction problem [@schratz2019].

Resampling objects in \pkg{mlr3spatiotmpcv} inherit from and can be created from established object classes for geospatial data in R, including simple features (add a general reference, maybe Lovelace), which facilitates its integration into domain-specific workflows in the geospatial sciences. This includes support for geographic coordinate reference systems (CRS) and their respective distance measures in projected planar space or using great circle distances on the unprojected ellipsoid (corrrect???). Non-spatial data tables with coordinates as variables are also supported. If no projection is specified, World Geodetic System 1984 (WGS84, EPSG: 4326) will be assumed.

@@

```{r create task}
library(mlr3)
library(mlr3spatiotempcv)

>>>>

Within the \pkg{mlr3} ecosystem, partitioning strategies are represented by their own objects of class \texttt{Resampling}, of which most are available within \pkg{mlr3} itself (e.g. regular random CV) and other specialized ones (e.g. \texttt{TaskClassifST} or \texttt{TaskRegrST}) are defined in extension packages such as \pkg{mlr3spatiotempcv}.
In the ML pipeline, these objects define the data splits used for model evaluation and selection (hyperparameter tuning) by ML algorithms.
They play an important role for an unbiased application of ML algorithms [@schratz2019].

Resampling objects in \pkg{mlr3spatiotmpcv} inherit from class \texttt{mlr3::Resampling} and can be created from established object classes for geospatial data in R, including simple features [@pebesma2018], which facilitates its integration into domain-specific workflows in the geospatial sciences.
This includes support for geographic coordinate reference systems (CRS) and their respective distance measures in projected planar space or using great circle distances on the unprojected ellipsoid.
Non-spatial data tables with coordinates as variables are also supported.
If no projection is specified, World Geodetic System 1984 (WGS84, EPSG: 4326) will be assumed.

@@

```{r create-task}
library(mlr3)
library(mlr3spatiotempcv)
